\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{a4wide}\title{Industrial project description (put the project title here)}
%\author{not specified}
\date{}
\begin{document}
\maketitle

%\begin{abstract}
Answer the question to outline your project. Choose one of the roles: an {Expert} or an~\textbf{Analyst}.
%\end{abstract}
% \paragraph{Keywords:} The Art On Scientific Research, Abstract Reconstruction, Please Put Yours 


\section{Planning the industrial research project}
Before planning the research, the analyst and (\textbf{expert}) discuss the key issues. After the long dash~--- our remarks.

\begin{enumerate}
\item Goal of the project. (\textbf{Expected development result.})~---
Expected research objective.
\item Applied problem solved in the project. (\textbf{How will the result be used?})~--- How to illustrate the result?
\item Description of historical measured data. (\textbf{Formats and timing.})~--- Algebraic data structure.
\item Quality criteria. (\textbf{How is the quality of the obtained result measured, what is in the report?})~--- Error function to optimize.
\item Project feasibility. (\textbf{How to show that the project is feasible, list of possible risks.})~--- Error analysis plan.
\item Conditions necessary for successful project implementation. (\textbf{Organization of work.})~--- Requirements for the data set.
\item Solution methods. (\textbf{Procedure libraries.})~--- Hypotheses, optimal probability models.
\end{enumerate}

\section{Research or development?}
In other words, novelty or technological advancement?

{Analyst:} What impact will the research have on the field of knowledge? How useful will it be?

{Expert:} (\textbf{How long will the model be used? What will replace it in the future?})

%\bibliographystyle{unsrt}
%\bibliography{Name-theArt}
\end{document}